\documentclass[a4paper,11pt]{scrreprt} 
%\usepackage[ngerman]{babel}
\usepackage[utf8x]{inputenc} 

%\usepackage{etoolbox}
%\usepackage[svgnames]{xcolor}

%\usepackage{tikz}

%\usepackage{framed}

\usepackage{libertine} % or any other font package
%\newcommand*\quotefont{\fontfamily{LinuxLibertineT-LF}} % selects Libertine as the quote font

\usepackage{tikz}
\usetikzlibrary{shadows}

\newcommand*\keystroke[1]{%
  \tikz[baseline=(key.base)]
    \node[%
      draw,
      fill=white,
      drop shadow={shadow xshift=0.25ex,shadow yshift=-0.25ex,fill=black,opacity=0.75},
      rectangle,
      rounded corners=1pt,
      inner sep=1.5pt,
      line width=0.5pt,
      font=\scriptsize%\sffamily
    ](key) {#1\strut}
  ;
}

\usepackage{fullpage}

\makeindex 
\begin{document}
\tableofcontents
\chapter{Getting started}
\section{Roleplaying}

There are numerous opinions and lessons describing role play. This one doesn't claim to be exhaustive nor sole validity. Always remember:
\begin{center}
\fbox{
\emph{You play a role. You are not the character you are playing.}}
\end{center}

The character you are playing should have the following characteristics: 
\begin{table}[h]
\begin{tabular}{ l p{12.5cm}}
Background story & You don't need a novel but some basic points should be 
defined. The empty parts in your story will fill in with time by 
itself. \\
(Dis-) Advantages & Nobody is only a bright hero and nobody loses all the 
time. Your character should have some positive as well as some negative attributes. \\
Goals & Your character should have a dream, something he or she 
wants to achieve desperately. \\
Phobia & There should be something he or she hates or fears. \\
Distinctiveness & Your character should have a quirk. It should be some distinctive feature, e.g. that could be a tiny voice, a 
special greeting or a preference for yellow hats. 
\end{tabular}
\end{table}

Please bear in mind that your character starts in Illarion unskilled. He or she cannot be an experienced crafter or warrior from the very beginning\footnote{Especially for players with less experience with roleplaying games, the following archetypes are useful: A servant or maid, recently thrown out of service due to any minor delinquency or a crafter or mercenary in apprenticeship on walk.}.
Give your counterpart a chance for reaction instead of forcing him or her into a situation. Don't pull her on her sleeve, \emph{try} to pull instead. A good role player will know how wo react properly. This especially holds for thievery or robberies, which makes playing villains rather difficult and requires some experience with role playing.

You may find a larger role play advice as well as background stories on our web page. 

\section{Story/Setting/Lore}
\subsection{Factions}
Illarion's people are divided into three different factions. Every inhabitant of the world of Illarion has to belong to either of these---or be entirely factionless. Every faction is based in a distinct, name-giving town. Each of these towns have crafts being associated with them while other crafts are missing entirely in these towns.
\paragraph{Cadomyr}
Cadomyr is a desert stronghold in the southwest of Illarion and it was founded by humans and lizards. It is the town of honor and knights, earls, baroness and knights should feel 
well settled here. It is ruled by her majesty Queen Rosaline Edwards.

Cadomyr's colors are red and white, its emblem shows a horned lion. 

\paragraph{Galmair}
Galmair is a town in the mountain town in the north of Illarion. Its first settlers were dwaves and 
orcs. It's the town of money; smiths, merchants and miner prefer this settlement. It is ruled by Don Vallerio 
Guillamo.

Galmair's colors are black and yellow, its emblem shows a winged pig. 

\paragraph{Runewick}
Runewick is a sea town in the south east of Illarion and was founded by halflings and elves.
It is the town of knowledge, scholars and their students can find enough libraries around. 
It is ruled by Archmage Elvaine Morgan.

Runewick's colors are blue and silver and the emblem shows a double headed eagle.

\subsection{Races}
There are five different playable races in Illarion which you can chose. They differ not only in the looks, but also in their behaviour, their preferences and their physical and mental abilities (attributes).
\paragraph{Humans}
\paragraph{Elves}
\paragraph{Dwarves}
\paragraph{Halflings}
\paragraph{Lizardmen}


\section{System requirements}
\section{Create an account}
Loginname: 5-34 characters
Meanings
\section{Create a character}
\subsection{Races, Attributes, Skills and all that}
\section{Install the client and log in}

\chapter{Controls}
\section{Moving around}
You can move your character (walk or run) across the map by mouse or by keyboard. 
The character follows the mouse pointer whenever the left mouse button is pressed and held down. Mostly, he or she will 
avoid obstacles automatically. 
Double click  on a free tile (meadow, way, rock, plaster) and your character will start walking walking
to that tile. 
To exactly move your character try using the keyboard:
\begin{table}[h]
\begin{tabular}{ l p{14.5cm}}
\keystroke{W}, \keystroke A, \keystroke S, \keystroke D & Main directions \\
\keystroke{$\uparrow$}, \keystroke{$\downarrow$}, \keystroke{$\leftarrow$}, \keystroke{$\rightarrow$} & Main directions. Diagonal directions are possible using 2 keys simultanuously  \\
Numpad & Main and diagonal directions \\
\keystroke{Alt} + arrow key & Your character turns in place \\
\keystroke{AltGr} + arrow key & Your character will run into the desired direction 
\end{tabular}
\end{table}

Beware: Your character can't run if he or she is overloaded (``A heavy load slows you 
down''). 
Eventually, some keyboard keys are used by your operating system already (e.g. Alt Gr and up arrow turns the screen upside down)

\section{Talking/Chatting}
Illarion emphasizes real roleplay. The basic interaction with other players as well as with NPCs 
takes place in the chat mode. The \keystroke{Return} key switches the chat mode on and off.

There are several different chat modes which can be enabled by typing \# and some command in front of your text:
\begin{table}[h]
\begin{tabular}{ l p{14.5cm}}
\#me & Character descriptions. 
You show unaudible emotions or descriptions of your character. The text is displayed in yellow. 
e.g.  ``\#me laughs'' becomes ``Paul laughs'', ``\#me stinks'' becomes ``Paul stinks'' \\
\#w & Whispering. Your words can be heard to the next but one tile. Whispered text is shown in Grey. \\
\#s & Shout. 
Your voice can be heard over a long distance. The text will be displayed in red. \\
\#o & OOC (Out of Character). 
You use this to indicate that it is not your character talking but the player behind it. The text 
is displayed in double brackets in grey. Only characters standing close by can hear this kind of comments.
\end{tabular}
\end{table}

\subsection{Languages}
There are six different languages that are spoken in Illarion. Everyone knows the common language, but the race specific languages are spoken and understood by the respective races only\footnote{The technical implementation of this feature is not yet finished. Currently, anyone can see everyones spoken text, independently of the language spoken.}. To switch the language your character is talking, use:
\begin{table}[h]
\begin{tabular}{ l l}
!lcommon & Common language \\
!ldwarf & Dwarf language \\
!lelf & Elf language \\
!lhalfling & Halfling language \\
!lhuman & Human language \\
!llizard & Lizard language
\end{tabular}
\end{table}


\section{Use}
\section{Fight}
\section{Trade}

\chapter{Game mechanics}
\section{Gathering}
\section{Crafting}
\section{Druidry}
\section{Trasures, Gems, Explorers Guild}

\chapter{(FAQ)}
\end{document}